From OpenACC to OpenMP 4: \\ Toward Automatic Translation

### 2016-04-29 paper.tex
Related work

Most related to our work is a talk by Oscar Hernandez et al.\@ at
OpenMPCon~2015~\cite{hernandez,hernandezvideo}.  This talk describes the
salient differences between OpenACC~2.0 and OpenMP~4.0 and suggests a
(manual) procedure for porting code from OpenACC to OpenMP\@.  Their procedure
consists of five steps: removing constructs with no OpenMP counterparts (like
\emph{kernels}), translating data regions, translating data updates, translating
accelerator parallel regions, and adjusting function attribute specifiers.

@@

%\newpage

>>>>

Most related to our work is a talk by Hernandez et al.\@ at
OpenMPCon~2015~\cite{hernandez,hernandezvideo}.  This talk describes the
salient differences between OpenACC~2.0 and OpenMP~4.0 and suggests a
(manual) procedure for porting code from OpenACC to OpenMP\@.  Their procedure
consists of five steps: removing constructs with no OpenMP counterparts (like
\emph{kernels}), translating data regions, translating data updates, translating
accelerator parallel regions, and adjusting function attribute specifiers.

%Several directive-based GPU programming models have been proposed over the year to characterize parallel program. 
Lee and Vetter~\cite{lee2012early} evaluate existing directive-based models and
show that directive-based models can achieve reasonable performance compared to
hand-written GPU codes. For accelarator programming, the two most promising
options are OpenACC and OpenMP.  Wienke et al.~\cite{wienke2014pattern} compare
both models with respect to their programmability to assist developers in
deciding which approach to take.  Xu and colleagues~\cite{xu2013exploring}
demonstrate the effectiveness of a hybrid model combined with OpenACC and
OpenMP as a plausible solution to port scientific applications in heterogeneous
architectures.

%In our work we describe the context for porting OpenACC device directives to OpenMP directives. And proposed an automated tool (with a small manual intervention) to port OpenACC into OpenMP.

\newpage

@@
